### 2018-09-10 ICRA19/covControl.tex
made the file not 17mb

Assume an obstacle-free, bounded, unit-size, square workspace. 
 As shown in Fig.~\ref{fig:SquareFill}, the maximum correlation occurs when the swarm is pushed in the direction $\beta = 3\pi/4$. 
 This correlation as a function of swarm area $A$ is never larger than 1/2, and the maximum correlation decays to 0 as $A$ grows to 1. By  \eqref{eq:covAndcorrInSquareWorkspace}, this maximum correlation is
\begin{align} \label{eq:GravityCorrelation}
\rho_{xy} =  \begin{cases}  \frac{1}{2}  , &  0\le A\le \frac{1}{2}  \\
% \frac{3 A (2 (A-2) A+1)}{4 A \left(A^2+3 \sqrt{2-2 A}-6\right)-12 \sqrt{2-2 A}+17}-1
 \frac{3 A (2 (A-2) A+1)}{4 A^3-24 A+\sqrt{2} (12 A-12) \sqrt{1-A}+17}-1
 , & \frac{1}{2} \le A\le 1
\end{cases}.
\end{align}
 If friction obeys the linear boundary layer model of \eqref{eq:boundarylayerflow} with boundary layer thickness $h$ and maximum friction $F_f$ equal to the maximum applied force $F$, we can generate  larger correlations.
 If the swarm size is smaller than $\approx 0.43$ and the boundary layer is sufficiently thick we can generate correlations larger than 1/2  using boundary friction.

 Assume that the swarm is initialized in the lower-left corner, in a rectangle of width $w$ and height $A/w$. 
 Such a rectangular configuration can be accomplished using the variance controllers from \cite{ShahrokhiIROS2015}. 
  If the swarm is then commanded to move a distance $L$ to the right, components of the swarm outside the boundary friction layer of height $h$ move further than components near the boundary. 
   The swarm is contained in a region $R$ composed of no more than three stacked components: at bottom a parallelogram inclined to the right top, at middle a rectangle, and at top a parallelogram inclined to the left top. These regions can be defined by the rectangle's left side, bottom, and top:
\begin{align}
r_{\text{left}} &= \min (L,1-w),\nonumber \\
r_{\text{bottom}} &=\min \left(\frac{A}{w}, h\frac{r_{\textrm{left}}}{L}  \right) \text{and}\nonumber \\
r_{\text{top}}  &= \min \left(\frac{A}{w}, 1-h\frac{r_{\text{left}}}{L}  \right).
\end{align}
If $\frac{A}{w} \le r_{\text{top}}$ the top parallelogram has no area. 
 Similarly, if $r_{\text{top}} \le r_{\text{bottom}}$ the rectangle has no area. 
The mean, variance, and correlation are calculated  using \eqref{eq:meanInSquareWorkspace}, \eqref{eq:varInSquareWorkspace}, and \eqref{eq:covAndcorrInSquareWorkspace} over the region $R$:
\begin{align} \iint_R f(x,y) \, dx \,dy &=  \int_0^{r_{\text{bottom}}}  \int_{\frac{L}{h}y}^{\frac{L}{h}y+w}  f(x,y)  dx \, dy \label{eq:correlationFriction} \\
&+\int_{r_{\text{bottom}}}^{r_{\text{top}}} \int_{r_{\text{left}}}^{r_{\text{left}} +w} f(x,y)    dx \, dy \nonumber\\
&+\int_{r_{\text{top}}}^{\frac{A}{w}} \int_{-\frac{L (y-r_{\text{top}})}{h}+r_{\text{left}}}^{r_{\text{left}}+w-\frac{L (y-r_{\text{top}})}{h}} f(x,y)   dx \, dy .\nonumber
\end{align}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{ControlledCorrelation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:ControlledCorrelation}
Analytical results comparing maximum correlation $\rho_{xy}$ under the boundary layer friction model of \eqref{eq:correlationFriction} with four boundary layer thicknesses $h$ and the stable triangular configuration \eqref{eq:GravityCorrelation}.
}\vspace{-1em}
\end{figure}

\section{Experiments}

@@

In this section we vary the force and approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. Kilobot is a three centimeter low cost robot that has light sensor. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}. Figure \ref{fig:kilobotAngle} shows angle of repose of the Kilobots with three different angles of the pink rod when the rod has 0$^\circ$, 22.5$^\circ$ and 45$^\circ$. The green lines show the triangle that the robots pile up. The cyan star is the center of mass of the rod, and mean position and variance of the robots are shown with a red star and red ellipse.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\caption{\label{fig:SetUp}
The platform where we control Kilobots with lights.
}
\end{figure}

>>>>

Assume an obstacle-free, bounded, unit-size, square workspace. 
 As shown in Fig.~\ref{fig:SquareFill}, the maximum correlation occurs when the swarm is pushed in the direction $\beta = 3\pi/4$. 
 This correlation as a function of swarm area $A$ is never larger than 1/2, and the maximum correlation decays to 0 as $A$ grows to 1. By  \eqref{eq:covAndcorrInSquareWorkspace}, this maximum correlation is
\begin{align} \label{eq:GravityCorrelation}
\rho_{xy} =  \begin{cases}  \frac{1}{2}  , &  0\le A\le \frac{1}{2}  \\
% \frac{3 A (2 (A-2) A+1)}{4 A \left(A^2+3 \sqrt{2-2 A}-6\right)-12 \sqrt{2-2 A}+17}-1
 \frac{3 A (2 (A-2) A+1)}{4 A^3-24 A+\sqrt{2} (12 A-12) \sqrt{1-A}+17}-1
 , & \frac{1}{2} \le A\le 1
\end{cases}.
\end{align}
 If friction obeys the linear boundary layer model of \eqref{eq:boundarylayerflow} with boundary layer thickness $h$ and maximum friction $F_f$ equal to the maximum applied force $F$, we can generate  larger correlations.
 If the swarm size is smaller than $A \approx 0.43$ and the boundary layer is sufficiently thick we can generate correlations larger than 1/2  using boundary friction.

 Assume that the swarm is initialized in the lower-left corner, in a rectangle of width $w$ and height $A/w$. 
 Such a rectangular configuration can be accomplished using the variance controllers from \cite{ShahrokhiIROS2015}. 
  If the swarm is then commanded to move a distance $L$ to the right, components of the swarm outside the boundary friction layer of height $h$ move further than components near the boundary. 
   The swarm is contained in a region $R$ composed of no more than three stacked components: at bottom a parallelogram inclined to the right top, at middle a rectangle, and at top a parallelogram inclined to the left top. These regions can be defined by the rectangle's left side, bottom, and top:
\begin{align}
r_{\text{left}} &= \min \left(L,1-w \right),\nonumber \\
r_{\text{bottom}} &=\min \left(\frac{A}{w}, h\frac{r_{\textrm{left}}}{L}  \right) \text{and}\nonumber \\
r_{\text{top}}  &= \min \left(\frac{A}{w}, 1-h\frac{r_{\text{left}}}{L}  \right).
\end{align}
If $\frac{A}{w} \le r_{\text{top}}$ the top parallelogram has no area. 
 Similarly, if $r_{\text{top}} \le r_{\text{bottom}}$ the rectangle has no area. 
The mean, variance, and correlation are calculated  using \eqref{eq:meanInSquareWorkspace}, \eqref{eq:varInSquareWorkspace}, and \eqref{eq:covAndcorrInSquareWorkspace} over the region $R$:
\begin{align} \iint_R f(x,y) \, dx \,dy &=  \int_0^{r_{\text{bottom}}}  \int_{\frac{L}{h}y}^{\frac{L}{h}y+w}  f(x,y)  dx \, dy \label{eq:correlationFriction} \\
&+\int_{r_{\text{bottom}}}^{r_{\text{top}}} \int_{r_{\text{left}}}^{r_{\text{left}} +w} f(x,y)    dx \, dy \nonumber\\
&+\int_{r_{\text{top}}}^{\frac{A}{w}} \int_{-\frac{L (y-r_{\text{top}})}{h}+r_{\text{left}}}^{r_{\text{left}}+w-\frac{L (y-r_{\text{top}})}{h}} f(x,y)   dx \, dy .\nonumber
\end{align}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{ControlledCorrelation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:ControlledCorrelation}
Analytical results comparing maximum correlation $\rho_{xy}$. Lines labeled \textsf{F} use the boundary layer friction model of \eqref{eq:correlationFriction} with four boundary layer thicknesses $h$ and the stable triangular configuration \eqref{eq:GravityCorrelation}.
}\end{figure}

\section{Experiments}\label{sec:Experiments}

@@

In this section we vary the force and approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a three-centimeter diameter,  low-cost robot with a light sensor. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}. Figure \ref{fig:kilobotAngle} shows angle of repose of the Kilobots with three different angles of the pink rod when the rod has 0$^\circ$, 22.5$^\circ$ and 45$^\circ$. The green lines show the triangle that the robots pile up. The cyan star is the center of mass of the rod, and mean position and variance of the robots are shown with a red star and red ellipse.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\caption{\label{fig:SetUp}
The platform where we control Kilobots with lights.
}
\end{figure}

### 2018-09-10 ICRA19/intro.tex
removed word robots.  If it shows up again we will know who to blame.
made the file not 17mb

   \textcolor{red}{TODO: lets do some experiments with salt in 3D printed shapes (or laser cut). Salt is micro scale, and roughly uniform (I think) we can get different magnitudes of global force by varying the tilt angle.}

@@

Shape control of many particles is essential for navigation, construction, and conveying information. 
 The small size of the particles makes it hard or even impossible to control each particle position individually. Instead, these particles are controlled with a single global control input.
 In previous work, we illustrated algorithms that could adjust the position of two particles in an environment with walls that have non-slip contacts \cite{shahrokhi2017}. We assumed that if a particle is touching a wall, it will stay still until the uniform input pull it from the wall. This work analyses interactions between the boundary and the particle swarm to shape shape of the swarm. In \cite{shahrokhi2018TRO} we showed how to control swarm statistics including mean position and variance. This work extends that work to shape control.

@@

The paper is arranged as follows. 
After a review of recent related work in Sec.  \ref{sec:RelatedWork},
 %Sec. \ref{subsec:FluidInTank} provides analytical position control results of stable configurations in two canonical workspaces with frictionless walls.  These results are limited in the set of shapes that can be generated.  To extend the range of possible shapes,
  Sec.  \ref{sec:angle} introduces angle of repose, a parameter of the particle swarm that can be used for shape control. 
Section  \ref{sec:covControl} describes implementations of the algorithms of covariance control in simulation and hardware experiments. 
 % Sec.  \ref{sec:expResults} 
 We end with directions for future research in Sec.  \ref{sec:conclusion}.

>>>>

@@

Shape control of many particles is essential for navigation, construction, and conveying information. 
 The small size of the particles makes it hard or even impossible to control each particle's position individually. Instead, these particles are often controlled with a single global control input.
 In previous work, we gave algorithms that could adjust the position of two particles in an environment with walls that have non-slip contacts~\cite{shahrokhi2017}. We assumed that if a particle is pushed into a wall, it will not move until a uniform input pulls it from the wall.
   This work analyses interactions between the rigid obstacles and the particles to control the configuration of the particles.
    % In \cite{shahrokhi2018TRO} we showed how to control swarm statistics including the mean position and variance. 
    % This work extends that work to shape control.

@@

The paper is arranged as follows. 
After a review of recent related work in Sec.~\ref{sec:RelatedWork},
  Sec.~\ref{sec:angle} introduces angle of repose, a parameter of the particle swarm that can be used for shape control. 
Section \ref{sec:covControl} provides analytical position control results of stable configurations in two canonical workspaces with frictionless walls.  These results are limited in the set of shapes that can be generated.  To extend the range of possible shapes, the section explores using linear boundary friction.
%describes implementations of the algorithms of covariance control in simulation and hardware experiments. 
 % Sec.  \ref{sec:expResults} 
 Hardware experiments and results are presented in Sec.~\ref{sec:Experiments}.
 We end with directions for future research in Sec.  \ref{sec:conclusion}.
